### 2020-09-16 priority-cp.tex
Finished theory skeleton.
Renamed SC rules, added PCP-SC.
Added reduction for PCP.
Added PCP reduction.
quick general pass to the paper
Proved lemma. Renamed rules.
some text on types

\subsection{Syntax}

\subsubsection{Priorities, types, and environments}
\[
\begin{array}{lcl}
  \ty{A}, \ty{B}, \ty{C}
  & \coloneqq & \ty{\tyone[\cs{o}]}
    \sep        \ty{\tybot[\cs{o}]}
    \sep        \ty{\tynil[\cs{o}]}
    \sep        \ty{\tytop[\cs{o}]}
    \sep        \ty{\tytens[\cs{o}]{A}{B}}
    \sep        \ty{\typarr[\cs{o}]{A}{B}}
    \sep        \ty{\typlus[\cs{o}]{A}{B}}
    \sep        \ty{\tywith[\cs{o}]{A}{B}}
  \\
  \ty{\Gamma}, \ty{\Delta}
  & \coloneqq & \ty{\emptyenv}
    \sep        \ty{\Gamma}, \tmty{x}{A}
\end{array}
\]
\[
\begin{array}{lcl}
  \ty{\co{(\tyone[\cs{o}])}} & = & \ty{\tybot[\cs{o}]} \\
  \ty{\co{(\tybot[\cs{o}])}} & = & \ty{\tyone[\cs{o}]} \\
  \ty{\co{(\tynil[\cs{o}])}} & = & \ty{\tytop[\cs{o}]} \\
  \ty{\co{(\tytop[\cs{o}])}} & = & \ty{\tynil[\cs{o}]}
\end{array}
\qquad
\begin{array}{lcl}
  \ty{\co{(\tytens[\cs{o}]{A}{B})}} & = & \ty{\typarr[\cs{o}]{\co{A}}{\co{B}}} \\
  \ty{\co{(\typarr[\cs{o}]{A}{B})}} & = & \ty{\tytens[\cs{o}]{\co{A}}{\co{B}}} \\
  \ty{\co{(\typlus[\cs{o}]{A}{B})}} & = & \ty{\tywith[\cs{o}]{\co{A}}{\co{B}}} \\
  \ty{\co{(\tywith[\cs{o}]{A}{B})}} & = & \ty{\typlus[\cs{o}]{\co{A}}{\co{B}}}
\end{array}
\]
\[
\begin{array}{lclclcl}
  \pr(\ty{\tyone[\cs{o}]})        & = & \cs{o}  \\
  \pr(\ty{\tybot[\cs{o}]})        & = & \cs{o}  \\
  \pr(\ty{\tynil[\cs{o}]})        & = & \cs{o}  \\
  \pr(\ty{\tytop[\cs{o}]})        & = & \cs{o}  \\
  \\
  \minpr(\ty{\emptyenv})          & = & \varnothing
\end{array}
\qquad
\begin{array}{lclclcl}
  \pr(\ty{\tytens[\cs{o}]{A}{B}}) & = & \cs{o}  \\
  \pr(\ty{\typarr[\cs{o}]{A}{B}}) & = & \cs{o}  \\
  \pr(\ty{\typlus[\cs{o}]{A}{B}}) & = & \cs{o}  \\
  \pr(\ty{\tywith[\cs{o}]{A}{B}}) & = & \cs{o}  \\
  \\
  \minpr(\ty{\Gamma},\tmty{x}{A}) & = & \minpr(\ty{\Gamma})\sqcap\minpr(\ty{A})
\end{array}
\]

@@

>>>>

\begin{figure}[t]
  \centering
  \includegraphics[width=0.8\columnwidth]{scheduler}
  \vspace{-4mm}
  \caption{Cyclic Scheduler from \cite{DardhaG18}}
  \label{fig:scheduler}
  \vspace{-4mm}
  \end{figure}

In this section we present an updated version of Priority CP \cite{DardhaG18}, which is Wadler's Classical Processes \cite{W12} with \emph{priorities}.
Some details of the calculus are inspired by Carbone \emph{et al.} \cite{CLMSW16} and Caires and P\'{e}rez \cite{CP17}.

\subsection{Syntax}
\subsubsection{Priorities, types, and environments}
Types are based on CLL and range over $\ty{A}, \ty{B}, \ty{C}$.
Types are annotated with priorities which range over $\cs{o} \in \mathbb{N} \sqcup \{\omega\}$.
Let $\omega$ be a special element such that $\cs{o}<\omega$ for all $\cs{o}\in \mathbb{N}$.
Often, we will omit $\omega$ when not necessary.
\todo{check the omega thing is also part of our presentation}
Types $\ty{\tyone[\cs{o}]}$ and $\ty{\tybot[\cs{o}]}$
are used to type channel endpoints which are ready to be closed.
Types $\ty{\tynil[\cs{o}]}$ and $\ty{\tytop[\cs{o}]}$ are used to... 
Type $\ty{\tytens[\cs{o}]{A}{B}}$ (respectively, $\ty{\typarr[\cs{o}]{A}{B}}$) is used to type a channel endpoint that first {outputs} (respectively, {inputs}) a channel of type $\ty A$ and then proceeds as $\ty B$.
$\ty{\typlus[\cs{o}]{A}{B}}$ is used to type a channel endpoint over which we can {select} either the \emph{left} branch and proceed as $\ty A$ or the \emph{right} branch and proceed as $\ty B$.
$\ty{\tywith[\cs{o}]{A}{B}}$ is used to type a channel endpoint that can offer a both $\ty A$ and $\ty B$.
A typing context $\ty\Gamma$ is a partial function associating channel names to types.
\[
\begin{array}{lcl}
  \ty{A}, \ty{B}, \ty{C}
  & \coloneqq & \ty{\tyone[\cs{o}]}
    \sep        \ty{\tybot[\cs{o}]}
    \sep        \ty{\tynil[\cs{o}]}
    \sep        \ty{\tytop[\cs{o}]}
    \sep        \ty{\tytens[\cs{o}]{A}{B}}
    \sep        \ty{\typarr[\cs{o}]{A}{B}}
    \sep        \ty{\typlus[\cs{o}]{A}{B}}
    \sep        \ty{\tywith[\cs{o}]{A}{B}}
  \\
  \ty{\Gamma}, \ty{\Delta}
  & \coloneqq & \ty{\emptyenv}
    \sep        \ty{\Gamma}, \tmty{x}{A}
\end{array}
\]

Duality on types is a total function and is defined below. It preserves priorities of types.
\[
\begin{array}{lcl}
  \ty{\co{(\tyone[\cs{o}])}} & = & \ty{\tybot[\cs{o}]} \\
  \ty{\co{(\tybot[\cs{o}])}} & = & \ty{\tyone[\cs{o}]} \\
  \ty{\co{(\tynil[\cs{o}])}} & = & \ty{\tytop[\cs{o}]} \\
  \ty{\co{(\tytop[\cs{o}])}} & = & \ty{\tynil[\cs{o}]}
\end{array}
\qquad
\begin{array}{lcl}
  \ty{\co{(\tytens[\cs{o}]{A}{B})}} & = & \ty{\typarr[\cs{o}]{\co{A}}{\co{B}}} \\
  \ty{\co{(\typarr[\cs{o}]{A}{B})}} & = & \ty{\tytens[\cs{o}]{\co{A}}{\co{B}}} \\
  \ty{\co{(\typlus[\cs{o}]{A}{B})}} & = & \ty{\tywith[\cs{o}]{\co{A}}{\co{B}}} \\
  \ty{\co{(\tywith[\cs{o}]{A}{B})}} & = & \ty{\typlus[\cs{o}]{\co{A}}{\co{B}}}
\end{array}
\]

Finally, function $\pr(\cdot)$ defined over types returns the priority of that type; function $\minpr(\cdot)$ defined over typing contexts returns the \emph{minimum} priority of all types in that context.
Both functions are defined as expected below.
\[
\begin{array}{lclclcl}
  \pr(\ty{\tyone[\cs{o}]})        & = & \cs{o}  \\
  \pr(\ty{\tybot[\cs{o}]})        & = & \cs{o}  \\
  \pr(\ty{\tynil[\cs{o}]})        & = & \cs{o}  \\
  \pr(\ty{\tytop[\cs{o}]})        & = & \cs{o}  \\
  \\
  \minpr(\ty{\emptyenv})          & = & \varnothing
\end{array}
\qquad
\begin{array}{lclclcl}
  \pr(\ty{\tytens[\cs{o}]{A}{B}}) & = & \cs{o}  \\
  \pr(\ty{\typarr[\cs{o}]{A}{B}}) & = & \cs{o}  \\
  \pr(\ty{\typlus[\cs{o}]{A}{B}}) & = & \cs{o}  \\
  \pr(\ty{\tywith[\cs{o}]{A}{B}}) & = & \cs{o}  \\
  \\
  \minpr(\ty{\Gamma},\tmty{x}{A}) & = & \minpr(\ty{\Gamma})\sqcap\minpr(\ty{A})
\end{array}
\]

@@

\subsection{Operational Semantics}

\subsubsection{Structural congruence}
\begin{mathpar}
  \begin{array}{llcl}
    \LabTirName{SC-LnkSwp}   & \tm{\link{x}{y}}
                             & \equiv & \tm{\link{y}{x}}
    \\
    \LabTirName{SC-ResLnk}   & \tm{\res{x}{y}{\link{x}{y}}}
                             & \equiv & \tm{\halt}
    \\
    \LabTirName{SC-ResExt}   & \tm{\res{x}{y}{(\ppar{P}{Q})}}
                             & \equiv & \tm{\ppar{\res{x}{y}{P}}{Q}},
                                        \text{ if }{\tm{x},\tm{y}\notin\fv(\tm{Q})}
    \\
    \LabTirName{SC-ResSwp}   & \tm{\res{x}{y}{P}}
                             & \equiv & \tm{\res{y}{x}{P}}
    \\
    \LabTirName{SC-ResCom}   & \tm{\res{x}{y}{\res{z}{w}{P}}}
                             & \equiv & \tm{\res{z}{w}{\res{x}{y}{P}}}
    \\
    \LabTirName{SC-ParNil}   & \tm{\ppar{P}{\halt}}
                             & \equiv & \tm{P}
    \\
    \LabTirName{SC-ParCom}   & \tm{\ppar{P}{Q}}
                             & \equiv & \tm{\ppar{Q}{P}}
    \\
    \LabTirName{SC-ParAsc}   & \tm{\ppar{P}{(\ppar{Q}{R})}}
                             & \equiv & \tm{\ppar{(\ppar{P}{Q})}{R}}
  \end{array}
\end{mathpar}

\subsubsection{Reduction}
\begin{mathpar}
  \begin{array}{llcl}
    \LabTirName{E-Lnk}     & \tm{\res{x}{y}{(\ppar{\link{w}{x}}{P})}}
                           & \red & \tm{\subst{P}{w}{x}}
    \\
    \LabTirName{E-Snd}     & \tm{\res{x}{y}{(\ppar{\send{x}{z}{P}}{\recv{x}{w}{Q}})}}
                           & \red & \tm{\res{x}{y}{\res{z}{w}{(\ppar{P}{Q})}}}
    \\
    \LabTirName{E-End}     & \tm{\res{x}{y}{(\ppar{\close{x}{P}}{\wait{y}{Q}})}}
                           & \red & \tm{\ppar{P}{Q}}
    \\
    \LabTirName{E-Sel\textsubscript{1}}
                           & \tm{\res{x}{y}{(\ppar{\inl{x}{P}}{\offer{x}{Q}{R}})}}
                           & \red & \tm{\res{x}{y}{(\ppar{P}{Q})}}
    \\
    \LabTirName{E-Sel\textsubscript{2}}
                           & \tm{\res{x}{y}{(\ppar{\inr{x}{P}}{\offer{x}{Q}{R}})}}
                           & \red & \tm{\res{x}{y}{(\ppar{P}{R})}}
  \end{array}
  \\
  \inferrule*[lab=E-Res]{
    \tm{P}\red\tm{P'}
  }{\tm{\res{x}{y}{P}}\red\tm{\res{x}{y}{P'}}}

  \inferrule*[lab=E-Par]{
    \tm{P}\red\tm{P'}
  }{\tm{\ppar{P}{Q}}\red\tm{\ppar{P'}{Q}}}

  \inferrule*[lab=E-LiftSC]{
    \tm{P}\equiv\tm{P'}
    \\
    \tm{P'}\red\tm{Q'}
    \\
    \tm{Q'}\equiv\tm{Q}
  }{\tm{P}\red\tm{Q}}

\end{mathpar}
